---
title: "Satisfaction-with-Mobile-Payment-Integration-across-Various-Online-Transactions"
author: "Suero, Huervana, Ahumada"
date: "2024-04-18"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)

data <- read_csv("Suero_Huervana_Ahumada/CSV FILES/Survey.csv")

str(data)
summary(data)

head(data)
tail(data)


```
############################## DEMOGRAPHICS ##############################

AGE
```{r}
# Convert Age column to numeric
data <- data %>%
  mutate(Age = as.numeric(Age))

# Remove NA values in Age column
cleaned_data <- data %>%
  filter(!is.na(Age))

# Count and arrange the frequencies of ages
age_counts <- cleaned_data %>%
  count(Age) %>%
  arrange(Age)


age_plot <- ggplot(age_counts, aes(x = Age, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  labs(title = "Age frequency",
       x = "Age",
       y = "Frequency")+
  theme_minimal()


#ggsave("age_distribution_plot.png", plot = age_plot, width = 8, height = 6, dpi = 300)


```

GENDER
```{r}

library(dplyr)

# Replace "Gay" with "Others" in the Gender column
data <- data %>%
  mutate(Gender = ifelse(Gender == "Gay", "Others", Gender))


gender_freq <- data %>%
  count(Gender) %>%
  arrange(Gender)
gender_freq


gender_plot <- ggplot(gender_freq, aes(x = Gender, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  labs(title = "Gender Frequency",
       x = "Gender",
       y = "Frequency") +
  geom_text(aes(label = n), vjust = -0.5, size = 3) +
  theme_minimal()


##ggsave("gender_frequency_plot.png", plot = gender_plot, width = 8, height = 6)


```

OCCUPATION
```{r}

library(dplyr)

# Define valid occupations
valid_occupations <- c("Student", "Employed", "Unemployed", "Self Employed")

# Replace invalid occupations with "Others" in the Occupation column
data <- data %>%
  mutate(Occupation = ifelse(!(Occupation %in% valid_occupations), "Others", Occupation))


occupation_freq <- data %>%
  count(Occupation) %>%
  arrange(Occupation)


occupation_plot <- ggplot(occupation_freq, aes(x = Occupation, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  labs(title = "Occupation Frequency",
       x = "Occupation",
       y = "Frequency") +
  geom_text(aes(label = n), vjust = -0.5, size = 3) +
  theme_minimal()


#ggsave("occupation_frequency_plot.png", plot = occupation_plot, width = 8, height = 6)


```

ONLINE PAYMENT METHOD OR PLATFORM THEY USE
```{r}

payment_method_count <-data %>%
  count(`Which online payment method or platform do you primarily use for making purchases?`)


for (i in 1:nrow(payment_method_count)) {
  print(paste("The total number of individuals who primarily use", payment_method_count[i, "Which online payment method or platform do you primarily use for making purchases?"], "is:", payment_method_count[i, "n"]))
}

# Replace "secret" with "others"
data <- data %>%
  mutate(`Which online payment method or platform do you primarily use for making purchases?` = ifelse(`Which online payment method or platform do you primarily use for making purchases?` == "secret", "others", `Which online payment method or platform do you primarily use for making purchases?`))

payment_method_count <- data %>%
  count(`Which online payment method or platform do you primarily use for making purchases?`) %>%
  arrange(desc(n))

payment_method_plot <- ggplot(payment_method_count, aes(x = `Which online payment method or platform do you primarily use for making purchases?`, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  labs(title = "Payment Method Frequency",
       x = "Payment Method",
       y = "Frequency") +
  geom_text(aes(label = n), vjust = -0.5, size = 3) +
  theme_minimal()


#ggsave("payment_method_frequency_plot.png", plot = payment_method_plot, width = 8, height = 6)

```


HOW OFTEN AN INDIVIDUAL USE ONLINE PAYMENT
```{r}

payment_frequency_count <- data %>%
  count(`How often do you use online payment for making purchases?`)


for (i in 1:nrow(payment_frequency_count)) {
  print(paste("The total number of individuals who use online payment", payment_frequency_count[i, "How often do you use online payment for making purchases?"], "is:", payment_frequency_count[i, "n"]))
}


# Replace invalid frequency categories with "Others"
data <- data %>%
  mutate(`How often do you use online payment for making purchases?` = 
           case_when(
             `How often do you use online payment for making purchases?` %in% c("2-3 times a week", "4-6 times a week", "Daily", "Multiple times a day", "Once a week", "Rarely (Less than once a month)") ~ `How often do you use online payment for making purchases?`,
             TRUE ~ "Others"
           )
  )


payment_frequency_count <- data %>%
  count(`How often do you use online payment for making purchases?`) %>%
  arrange(desc(n))


payment_frequency_plot <- ggplot(payment_frequency_count, aes(x = `How often do you use online payment for making purchases?`, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  labs(title = "Payment Frequency Frequency",
       x = "Payment Frequency",
       y = "Frequency") +
  geom_text(aes(label = n), vjust = -0.5, size = 3) +
  theme_minimal()


#ggsave("payment_frequency_plot.png", plot = payment_frequency_plot, width = 8, height = 6)


```




############################## DETERMINANTS ##############################

CHANGING "Strong Disagree to "Strongly Disagree" (Error in making the survey)
```{r}


changed_data <- data

# Iterate through each row and replace "Strong Disagree" with "Strongly Disagree"
for (i in 1:nrow(changed_data)) {
  changed_data[i, ] <- lapply(changed_data[i, ], function(x) ifelse(x == "Strong Disagree", "Strongly Disagree", x))
}

# Print the updated dataframe
print(changed_data)

# Write changed_data to a CSV file
write_csv(changed_data, "changed_data.csv")


```


```{r}

question_columns <- c("PE1", "PE2", "PE3", "EE1", "EE2", "EE3", "AUT1", "AUT2", "AUT3", "AUT4", "SI1", "SI2", "FC1", "FC2", "FC3", "FC4","SE1", "SE2", "SE3", "A1", "A2", "A3", "A4")

```

CHANGING QUESTIONS TO FACTOR
```{r}

for (column_name in question_columns) {
  changed_data[[column_name]] <- factor(changed_data[[column_name]],
                              levels = c("Strongly Disagree", "Disagree", "Neutral", "Agree", "Strongly Agree"),
                              ordered = TRUE)
}

```

SEPARATING THE DEMOGRAPHICS AND DETERMINANTS
```{r}

demographic_cols <- c("Timestamp", "Email Address" ,"Score","Name", "Age", "Gender","Occupation","Address","Contact Number(Optional)", "Which online payment method or platform do you primarily use for making purchases?", "How often do you use online payment for making purchases?")
demographics <- changed_data %>% 
  select(all_of(demographic_cols))

demographic_cols

determinant_cols <- setdiff(names(changed_data), demographic_cols)
determinants <- changed_data %>% 
  select(all_of(determinant_cols))

determinant_cols

```

MAPPING EACH QUESTION TO ITS CORRESPONDING CATEGORY
```{r}

category_map <- list(
  "Performance Expectancy" = c("PE1", "PE2", "PE3"),
  "Effort Expectancy" = c("EE1", "EE2", "EE3"),
  "Attitude toward using technology" = c("AUT1", "AUT2", "AUT3", "AUT4"),
  "Social influence" = c("SI1", "SI2"),
  "Facilitating Conditions" = c("FC1", "FC2", "FC3", "FC4"),
  "Self-Efficacy" = c("SE1", "SE2", "SE3"),
  "Anxiety" = c("A1", "A2", "A3", "A4")
)

category_df <- stack(category_map)
colnames(category_df) <- c("question", "category")

```


CONVERT TO NUMERIC AND CALCULATE MEANS
CONVERT TO NUMERIC AND CALCULATE STANDARD DEVIATIONS
COMBINE MEANS, STANDARD DEVIATIONS, AND CATEGORIES
```{r}

determinants_means <- determinants %>%
  mutate(across(everything(), as.numeric)) %>%
  summarise_all(.funs = mean) %>% 
  pivot_longer(cols = everything(), names_to = "question", values_to = "mean")

determinants_sds <- determinants %>%
  mutate(across(everything(), as.numeric)) %>%
  summarise_all(.funs = sd) %>% 
  pivot_longer(cols = everything(), names_to = "question", values_to = "sd")


determinant_summary <- determinants_means %>%
  inner_join(determinants_sds, by = "question") %>%
  inner_join(category_df, by = "question")

determinant_summary

```

COMBINE MEANS AND STANDARD DEVIATIONS BY CATEGORY
```{r}

determinant_mean_by_category <- aggregate(mean ~ category, determinant_summary, mean)
determinant_sd_by_category <- aggregate(sd ~ category, determinant_summary, sd)

determinant_summary_by_category <- determinant_mean_by_category %>%
  inner_join(determinant_sd_by_category, by= "category")

determinant_summary_by_category

write.csv(determinant_summary_by_category, "determinantMeanSd.csv")

```


PLOTTING DETERMINANTS
```{r}
determinant_mean_sd <- read_csv("Suero_Huervana_Ahumada/CSV FILES/determinantMeanSd.csv")

# Define custom colors
my_colors <- c("Performance Expectancy" = "#FF6F61",
               "Effort Expectancy" = "#6B5B95",
               "Attitude toward using technology" = "#88B04B",
               "Social influence" = "#F7CAC9",
               "Facilitating Conditions" = "#92A8D1",
               "Self-Efficacy" = "#955251",
               "Anxiety" = "#FFA600")

# Plotting
determinant_plot <- ggplot(determinant_mean_sd, aes(x = category, y = mean, fill = category)) +
  geom_bar(stat = 'identity', color = "black") +
  geom_errorbar(aes(ymin = mean - sd, ymax = mean + sd), width = 0.4, position = position_dodge(0.9)) +
  labs(title = "Mean with Standard Deviation",
       x = "Category",
       y = "Mean") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none") +  # Remove legend
  scale_fill_manual(values = my_colors)  # Apply custom colors


#ggsave("determinant_mean_sd.png", plot = determinant_plot, width = 10, height = 6, dpi = 300)


determinant_plot

```